Measurement of total hadronic differential cross sections in the LArIAT experiment

### 2018-05-01 Chapter-3/3-TheLArIATExperiment.tex
s

\chapter{LArIAT: Liquid Argon In A Testbeam}\label{sec:experimentDescription}
In this chapter, we describe the LArIAT experimental setup. We start by illustrating the journey of the charge particles in the Fermilab accelerator complex, from the gaseous thermal hydrogen at the Fermilab ion source to the delivery of the LArIAT tertiary beam at MC7. We  then describe the LArIAT beamline detectors, the LArTPC, the DAQ and the monitoring system.

%\section{LArIAT \& the Intensity Frontier}
\section{The Particles Path to LArIAT}

LArIAT's particles history begins in the Fermilab accelerator complex with a beam of protons. The process of protons acceleration develops in gradual stages (see picture \ref{fig:Accelerator}): gaseous hydrogen is ionized in order to form H$^{-}$ ions; these ions are boosted to 750 keV by a Cockroft-Walton accelerator and injected to the Linac linear accelerator that increases their energy up to 400 MeV; then, H$^{-}$ ions pass through a carbon foil and lose the two electrons; the resulting protons are then injected into a rapid cycling synchrotron, called Booster; at this stage, protons reach 8 GeV of energy and are compacted into bunches; the next stage of acceleration is the Main Injector, a synchrotron which accelerates the bunches up to 120 GeV; in the Main Injector, several bunches are merged into one and are ready for delivery.

The Fermilab accelerator complex works in supercycles of roughly 60 seconds in duration. The beam is split by electrostatic septa and delivered at different experimental halls all over the lab. A 120~GeV primary proton beam with variable intensity is extracted in four-second ``spills" and sent to the Meson Center beam line.

LArIAT's home at Fermilab is the Fermilab Test Beam Facility (FTBF), where the experiment characterizes a beam of charge particles downstream from the Meson Center beam line. 
Here, the primary beam is focused onto a tungsten target to create LArIAT's secondary beam. The composition of the secondary particle beam is mainly positive pions. The momentum peak of the secondary beam was fixed at 64~GeV/c for the LArIAT data considered in this work, although the beam is tunable in momentum between 8-80\,GeV/c; this configuration of the secondary beamline assured a stable beam delivery at the LArIAT experimental hall.

The secondary beam impinges then on a copper target within a steel collimator inside the LArIAT experimental hall (MC7) to create the LArIAT tertiary beam, (shown in  Fig.~\ref{fig:tert-layout}).   The steel collimator selects particles produced with a $13^\circ$ production angle at the target down the beamline.  The particles are then bent by roughly $~10^\circ$  through a pair of dipole magnets.  By configuring the field intensity of the magnets we allow the particles of LArIAT's tertiary beam to span a momentum range from 0.2 to 1.4~GeV/c. The polarity of the magnet is also configurable and determines the sign of the beamline particles which are focused on the LArTPC. If the magnets polarity is positive the tertiary beam composition counts mostly pions and protons with a small fraction of electrons, muons, and kaons. It is the job of the LArIAT beamline detectors to select the particles polarity,  to perform particle identification in the beamline and to measure the momentum of the tertiary beam particles before they get to the LArTPC. The LArIAT detectors are described in the following paragraphs.

%\begin{comment}     
\begin{figure}
  \centering  	
\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Chapter-3/Images/AcceleratorFNAL.png}
\caption{Layout of Fermilab Acellerator complex.}
\label{fig:Accelerator}
\end{figure}

%\begin{comment}     
\begin{figure}
  \centering  	
\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Chapter-3/Images/Tertiary.png}
\caption{Bird's eye view of the LArIAT tertiary beamline. In grey: upstream and downstream collimators; in yellow: bending magnets; in red: wire chambers; in blue: time of flight; in green: liquid argon TPC volume; in maroon: muon range statck.}
\label{fig:tert-layout}
\end{figure}

@@

The key components of the tertiary beamline instrumentation for the hadron cross section analyses are the two bending magnets, a set of four wire chambers (WCs) and two time-of-flight scintillating paddles (TOF) and, of course, the LArTPC.  The magnets determine the polarity of the particles in the tertiary beam; the combination of magnets and wire chambers determines the particles' momentum, which is used to determine the particle species in conjunction with the TOF.
A muon range stack downstream from the TPC and two sets of cosmic paddles configured as a telescope surrounding the TPC are also used for calibration purposes.

@@

LArIAT uses a pair of identical Fermilab type ``NDB" electromagnets, recycled from the Tevatron's anti-proton ring, in a similar configuration used for the  MINERvA T-977 test beam calibration~\cite{MinervaTestbeam}. 
The magnets are a fundamental piece of the LArIAT beamline equipment, as they are used for both particle identification and momentum measurement before the LArTPC. The sign of the current in the magnets allows us to select either positively or negatively charged particles; the value of the magnetic field is used in the momentum determination and in the subsequent particle identification.

We describe here the characteristics and response of one magnet, as the second one has a similar response, given its identical shape and history. Each magnet is a box with a rectangular aperture gap in the center to allow for the particle passage.  The magnet aperture measures 14.224~cm in height, 31.75~cm in width, and  46.67~cm in length.  Since the wire chambers aperture ($\sim$12.8~cm$^2$) is smaller than the magnet aperture, only the central part of the magnet gap is utilized. The field is extremely uniform over this limited aperture and was measured with two hall probes, both calibrated with nuclear magnetic resonance probes. The probes measured the excitation curve shown in Figure~\ref{fig:magnet_excitation}.

@@

The current through the magnets at a given time is identical in both magnets. For the Run II data taking period, the current settings explored were 60A (B $\sim$0.21 T) and 100A (B $\sim$0.35 T) in both polarities. 
Albeit advantageous to enrich the tertiary beam composition with high mass particles such as kaons, we never pushed the magnets current over 100 A, not to incur in overheating.  During operation, we operated a air and water cooling system on the magnets and we remotely monitored the magnets temperature.

\subsection{Multi-Wire Proportional Chambers}\label{sec:MWPC}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\begin{centering}
\vspace{-0.3cm}
\includegraphics[height=2.3in]{Chapter-3/Images/WireChamber.png}
\caption{
{One of the four Multi Wire Proportional Chambers (WC) used in the LArIAT tertiary beamline and relative read-out electronics.}
}
\label{fig:wirechamber}
\end{centering}
\end{figure}

LArIAT uses four multi-wire proportional chambers, or wire chambers (WC) for short, two upstream and two downstream from the bending magnets. The geometry of one chamber is shown in Figure~\ref{fig:wirechamber}: the WC effective aperture is a square of  12.8~cm perpendicular to the beam direction.  Inside the chamber, the 128 horizontal and 128 vertical wires hang at a distance of 1~mm from each other in a mixture of 85\% Argon and 15\% isobutane gas.  The WC operating voltage is between 2400~V and 2500~V. The LArIAT wire chambers are an upgraded version of the Fenker Chambers~\cite{Fenker}, where an extra grounding improves the signal to noise ratio of the electronic readout.

Two ASDQ chips~\cite{ASDQchip} mounted on a mother board plugged into the chamber serve as front end amplifier/discriminator. The chips are connected to a multi-hit TDC~\cite{Sten} which provides a fast OR output used as first level trigger. The TDC time resolution is 1.18~ns/bin and can accept 2 edges per 9~ns.  
The maximum event rate acceptable by the chamber system is of 1 MHz: this rate is not a limiting factor considering that \textcolor{red}{the rate of the tertiary particle beam at the first wire chamber is estimated to be less than 15 kHz}. A full spill of data occurring once per supercycle is stored on the TDC board memory at once and read out by a specially designed controller.  We use LVDS cables to carry both power and data between the controller and the TDCs and from the controller to the rest of the DAQ.  
%It is possible to program the time window for acceptance for hits, time offsets, front end threshold, and pulse shaping parameters through the controller via a USB from a PC or through an Ethernet connection.

@@

where $B_{eff}$ is the effective maximum field in a square field approximation,  $L_{eff}$ is the effective length of both magnets (twice the effective length of one magnet), $\theta_{US}$ is the angle off the $z$ axis of the upstream trajectory, $\theta_{DS}$ is the angle off the $z$ axis of the downstream trajectory  and  3.3~$c^{-1}$ is the conversion factor from [T$\cdot$m] to [MeV/c]. By using the hit positions on the third and fourth wire chamber, we estimate the azimutal and polar angles of the particle trajectory, and we are able to calculate the other components of the momentum.

@@

\subsection{Time-of-Flight System}\label{sec:TOF}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Two scintillator paddles, one upstream to the first set of WCs and one downstream to the second set of WCs  form LArIAT  time-of-flight (TOF) detector system.

The upstream paddle is made of a 10 x 6 x 1~cm scintillator piece, read out by two PMTs mounted on the beam left side which collect the light from light guides mounted on all four edges of the scintillator. The downstream paddle is a   14 x 14 x 1~cm scintillator piece read out by two PMTs on the opposite ends of the scintillator.
The relatively thin width on the beamline direction minimizes energy loss of the particles coming from the target in the scintillator material.

@@

The TOF signals rise time (10-90\%) is 4 ns and a full width, half-maximum of 9 ns consistent in time. The signal amplitudes from the upstream TOF and  downstream TOF are slightly different:  200 mV for the upstream PMTs but only 50 mV for downstream PMTs. The time of the pulses was calculated utilizing an oversampled template derived from the data itself. We take the pulse pedestal from samples far from the pulse and subtract it to the pulse amplitude. We then stretch vertically a template to match the pedestal-subtracted pulse amplitude and we move it horizontally to find the time. With this technique, we find a pulse time-pickoff resolution better than 100 ps.  The pulse pile up is not a significant problem given the TOF timing resolution and the rate of the particle beam.  Leveraging on the pulses width uniformity of any given PMT,  we flag events where two pulses overlap as closely in time as 4 ns with an 90\% efficiency according to simulation.

We combine the pulses from the two PMTs on each paddle to determine the particles' arrival time by averaging the time measured from the single PMT, so to minimize errors due to optical path differences in the scintillator.  However, a time spread of approximately 300~ps is present in both the upstream and downstream detectors, likely due to transit time jitter in the PMTs themselves.  There is no evidence of systematic timing drift over long data-taking periods such as 3-4 months: the maximum variation of the average time differences between pairs of PMTs reading out the same scintillator is of the order of 150~ps.

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{Chapter-3/Images/DSTOF.jpg}
\caption{Image of the down stream time of flight paddle, PMTs and relative support structure before mounting. } 
\label{pic:cosmicpaddle}
\end{figure}

@@

The punch-thorough and the muon range stack (MuRS) detectors are located downstream of the TPC. These detectors provide a sample of  TPC crossing tracks without relying on TPC information and can be used to improve particle ID for  muons and pions with momentum higher than  450 MeV/c.

The punch-thorough is simple sheet of scintillator material, read out by two PMTs. 
The MuRS is a segmented block of steel with four slots instrumented with scintillation bars. The four steel layers in front of each instrumented slot are 2 cm, 2 cm, 14 cm and 16 cm wide in the beam direction. Each instrumented slot is equipped with four scintillation bars each, positioned horizontally in the direction orthogonal to the beam. Each scintillator bar measures  \textcolor{red}{? x ? x 2}~cm and it is read out by one PMT.

The signals from both the punch-thorough and the MuRS PMTs are digitized in the CAEN V1740, same as the TPC; the details of this discriminator are laid out in~\ref{sec:TPCCharge}. It is worth noticing that the sampling time of the CAEN V1740 is slow (of the order of 128 ns), so pulse shape information from the PMT is lost.
Punch-thorough and MuRS hits are formed utilizing the digital discriminator signals under threshold at a given time, where we obtain the threshold for each PMT directly on data distributions.

@@

\section{In the Cryostat}
\subsection{Cryogenics and Argon Purity}\label{ch:Cryo}
LArIAT repurposed the ArgoNeuT cryostat \cite{ArgoNeuT-det} in order to use it in a beam of charge particles, and added a new process piping and a new liquid argon filtration system in FTBF.  %The main modifications to the ArgoNeuT cryostat are the addition of a beam flange and a port for the light collection system, 
Inside the LArIAT experimental hall, the cryostat sits on the beam of charge particles with its horizontal main axis oriented parallel to the beam.

>>>>

\chapter{LArIAT: Liquid Argon In A Testbeam}\label{sec:experimentDescription}
In this chapter, we describe the LArIAT experimental setup. We start by illustrating the journey of the charged particles in the Fermilab accelerator complex, from the gaseous thermal hydrogen at the Fermilab ion source to the delivery of the LArIAT tertiary beam at MC7. We  then describe the LArIAT beamline detectors, the LArTPC, the DAQ and the monitoring system.

%\section{LArIAT \& the Intensity Frontier}
\section{The Particles' Path to LArIAT}

LArIAT's particle history begins in the Fermilab accelerator complex with a beam of protons. The process of proton acceleration develops in gradual stages (see picture \ref{fig:Accelerator}): gaseous hydrogen is ionized in order to form H$^{-}$ ions; these ions are boosted to 750 keV by a Cockroft-Walton accelerator and injected into the linear accelerator (Linac) that increases their energy up to 400 MeV; then, H$^{-}$ ions pass through a carbon foil and lose the two electrons; the resulting protons are then injected into a rapid cycling synchrotron, called the Booster; at this stage, protons reach 8 GeV of energy and are compacted into bunches; the next stage of acceleration is the Main Injector, a synchrotron which accelerates the bunches up to 120 GeV; in the Main Injector, several bunches are merged into one and are ready for delivery.

The Fermilab accelerator complex works in supercycles of  60 seconds in duration. A 120~GeV primary proton beam with variable intensity is extracted in four-second ``spills" and sent to the Meson Center beam line.  %The beam is split by electrostatic septa and delivered to different experimental halls all over the lab.

LArIAT's home at Fermilab is the Fermilab Test Beam Facility (FTBF), where the experiment characterizes a beam of charged particles in the Meson Center beam line. 
At FTBF, the primary beam is focused onto a tungsten target to create LArIAT's secondary beam. The secondary beamline is set such that the composition of the secondary particle beam is mainly positive pions. The momentum peak of the secondary beam was fixed at 64~GeV/c for the LArIAT data considered in this work, although the beam is tunable in momentum between 8-80\,GeV/c; this configuration of the secondary beamline assured a stable beam delivery at the LArIAT experimental hall.

The secondary beam impinges then on a copper target within a steel collimator inside the LArIAT experimental hall (MC7) to create the LArIAT tertiary beam, (shown in  Fig.~\ref{fig:tert-layout}).   The steel collimator selects particles produced with a $13^\circ$ production angle.   The particles are then bent by roughly $~10^\circ$  through a pair of dipole magnets.  By configuring the field intensity of the magnets we allow the particles of LArIAT's tertiary beam to span a momentum range from 0.2 to 1.4~GeV/c. The polarity of the magnet is also configurable and determines the sign of the beamline particles which are focused on the LArTPC. If the magnet polarity is positive the tertiary beam composition is mostly pions and protons with a small fraction of electrons, muons, and kaons. It is the job of the LArIAT beamline equipment to select the particles polarity,  to perform particle identification in the beamline and to measure the momentum of the tertiary beam particles before they get to the LArTPC. The LArIAT detectors are described in the following paragraphs.

%\begin{comment}     
\begin{figure}
  \centering  	
\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Chapter-3/Images/AcceleratorFNAL.png}
\caption{Layout of Fermilab Accelerator complex.}
\label{fig:Accelerator}
\end{figure}

%\begin{comment}     
\begin{figure}
  \centering  	
\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Chapter-3/Images/Tertiary.png}
\caption{Bird's eye view of the LArIAT tertiary beamline. In grey: upstream and downstream collimators; in yellow: bending magnets; in red: multi wire proportional chambers; in blue: time of flight; in green: liquid argon TPC volume; in maroon: muon range statck.}
\label{fig:tert-layout}
\end{figure}

@@

The key components of the tertiary beamline instrumentation for the hadron cross section analyses are the two bending magnets, a set of four wire chambers (WCs) and two time-of-flight scintillating paddles (TOF) and, of course, the LArTPC.  The magnets determine the polarity of the particles in the tertiary beam; the combination of magnets and wire chambers determines the particles' momenta, which is used to determine the particle species in conjunction with the TOF.
A muon range stack downstream from the TPC and two sets of cosmic paddles configured as a telescope surrounding the TPC are also used for calibration purposes.

@@

LArIAT uses a pair of identical Fermilab type ``NDB" electromagnets, recycled from the Tevatron's anti-proton ring, in a similar configuration used for the  MINERvA T-977 test beam calibration~\cite{MinervaTestbeam}. 
The magnets are a fundamental piece of the LArIAT beamline equipment, as they are used for the selection of the particle polarity and for the momentum measurement before the LArTPC. The sign of the current in the magnets allows us to select either positively or negatively charged particles; the value of the magnetic field is used in the momentum determination and in the subsequent particle identification.

We describe here the characteristics and response of one magnet, as the second one has a similar response, given its identical shape and history. Each magnet is a box with a rectangular aperture gap in the center to allow for the particle passage.  The magnet aperture measures 14.22~cm in height, 31.75~cm in width, and  46.67~cm in length.  Since the wire chambers aperture ($\sim$12.8~cm$^2$) is smaller than the magnet aperture, only the central part of the magnet gap is utilized. The field is extremely uniform over this limited aperture and was measured with two hall probes, both calibrated with nuclear magnetic resonance probes. The probes measured the excitation curve shown in Figure~\ref{fig:magnet_excitation}.

@@

The current through the magnets at a given time is identical in both magnets. For the Run II data taking period, the current settings explored were 60A (B $\sim$0.21 T) and 100A (B $\sim$0.35 T) in both polarities. 
Albeit advantageous to enrich the tertiary beam composition with high mass particles such as kaons, we never pushed the magnets current over 100 A, not to incur in overheating.  During operation, we operated an air and water cooling system on the magnets and we remotely monitored the magnet temperatures.

\subsection{Multi-Wire Proportional Chambers}\label{sec:MWPC}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\begin{centering}
\vspace{-0.3cm}
\includegraphics[height=2.3in]{Chapter-3/Images/WireChamber.png}
\caption{
{One of the four Multi Wire Proportional Chambers (WC) used in the LArIAT tertiary beamline and related read-out electronics.}
}
\label{fig:wirechamber}
\end{centering}
\end{figure}

LArIAT uses four multi-wire proportional chambers, or wire chambers (WC) for short, two upstream and two downstream from the bending magnets. The geometry of one chamber is shown in Figure~\ref{fig:wirechamber}: the WC effective aperture is a square of  12.8~cm perpendicular to the beam direction.  Inside the chamber, the 128 horizontal and 128 vertical wires strung at a distance of 1~mm from each other in a mixture of 85\% Argon and 15\% isobutane gas.  The WC operating voltage is between 2400~V and 2500~V. The LArIAT wire chambers are an upgraded version of the Fenker Chambers~\cite{Fenker}, where an extra grounding improves the signal to noise ratio of the electronic readout.

Two ASDQ chips~\cite{ASDQchip} mounted on a mother board plugged into the chamber serve as front end amplifier/discriminator. The chips are connected to a multi-hit TDC~\cite{Sten} which provides a fast OR output used as first level trigger. The TDC time resolution is 1.18~ns/bin and can accept 2 edges per 9~ns.  
The maximum event rate acceptable by the chamber system is 1 MHz: this rate is not a limiting factor considering that \textcolor{red}{the rate of the tertiary particle beam at the first wire chamber is estimated to be less than 15 kHz}. A full spill of data occurring once per supercycle is stored on the TDC board memory at once and read out by a specially designed controller.  We use LVDS cables to carry both power and data between the controller and the TDCs and from the controller to the rest of the DAQ.  
%It is possible to program the time window for acceptance for hits, time offsets, front end threshold, and pulse shaping parameters through the controller via a USB from a PC or through an Ethernet connection.

@@

where $B_{eff}$ is the effective maximum field in a square field approximation,  $L_{eff}$ is the effective length of both magnets (twice the effective length of one magnet), $\theta_{US}$ is the angle off the $z$ axis of the upstream trajectory, $\theta_{DS}$ is the angle off the $z$ axis of the downstream trajectory  and  3.3~$c^{-1}$ is the conversion factor from [T$\cdot$m] to [MeV/c]. By using the hit positions on the third and fourth wire chamber, we estimate the azimuthal and polar angles of the particle trajectory, and we are able to calculate the other components of the momentum.

@@

\subsection{Time-of-Flight System}\label{sec:TOF}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Two scintillator paddles, one upstream of the first set of WCs and one downstream of the second set of WCs  form LArIAT  time-of-flight (TOF) detector system.

The upstream paddle is made of a 10 x 6 x 1~cm scintillator piece, read out by two PMTs mounted on the beam left side which collect the light from light guides mounted on all four edges of the scintillator. The downstream paddle is a   14 x 14 x 1~cm scintillator piece read out by two PMTs on the opposite ends of the scintillator, as shown in figure \ref{fig:TOF}.
The relatively thin width in the beamline direction minimizes energy loss of beam particles traveling through the scintillator material.

@@

The TOF signals rise time (10-90\%) is 4 ns and a full width, half-maximum of 9 ns consistent in time. The signal amplitudes from the upstream TOF and  downstream TOF are slightly different:  200 mV for the upstream PMTs but only 50 mV for downstream PMTs. The time of the pulses was calculated utilizing an oversampled template derived from the data itself. We take the pulse pedestal from samples far from the pulse and subtract it from the pulse amplitude. We then vertically stretch  a template to match the pedestal-subtracted pulse amplitude and we move it horizontally to find the time. With this technique, we find a pulse time-pickoff resolution better than 100 ps.  The pulse pile up is not a significant problem given the TOF timing resolution and the rate of the particle beam.  Leveraging on the pulses width uniformity of any given PMT,  we flag events where two pulses overlap as closely in time as 4 ns with a 90\% efficiency according to simulation.

We combine the pulses from the two PMTs on each paddle to determine the particles' arrival time by averaging the time measured from the single PMT, so to minimize errors due to optical path differences in the scintillator.  However, a time spread of approximately 300~ps is present in both the upstream and downstream detectors, likely due to transit time jitter in the PMTs themselves.  %There is no evidence of systematic timing drift over long data-taking periods such as 3-4 months: the maximum variation of the average time differences between pairs of PMTs reading out the same scintillator is of the order of 150~ps.

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{Chapter-3/Images/DSTOF.jpg}
\caption{Image of the down stream time of flight paddle, PMTs and relative support structure before mounting. } 
\label{fig:TOF}
\end{figure}

@@

The punch-through and the muon range stack (MuRS) detectors are located downstream of the TPC. These detectors provide a sample of  TPC crossing tracks without relying on TPC information and can be used to improve particle ID for  muons and pions with momentum higher than  450 MeV/c.

The punch-through is simple sheet of scintillator material, read out by two PMTs. 
The MuRS is a segmented block of steel with four slots instrumented with scintillation bars. The four steel layers in front of each instrumented slot are 2 cm, 2 cm, 14 cm and 16 cm deep in the beam direction. Each instrumented slot is equipped with four scintillation bars each, positioned horizontally in the direction orthogonal to the beam. Each scintillator bar measures  \textcolor{red}{? x ? x 2}~cm and it is read out by one PMT.

The signals from both the punch-thorough and the MuRS PMTs  are sent to a NIM discriminator. If the signal crosses the discriminator threshold, it is digitized in the CAEN V1740, same as the TPC. The sampling time of the CAEN V1740 is slow (of the order of 128 ns) and that the pulse shape information from the PMT is lost. A Punch-thorough and MuRS signal will then be simply a ``hit" at a given time in the beamline event.

@@

\section{In the Cryostat}
\subsection{Cryogenics and Argon Purity}\label{ch:Cryo}
LArIAT repurposed the ArgoNeuT cryostat \cite{ArgoNeuT-det} in order to use it in a beam of charged particles, and added a new process piping and a new liquid argon filtration system in FTBF.  %The main modifications to the ArgoNeuT cryostat are the addition of a beam flange and a port for the light collection system, 
Inside the LArIAT experimental hall, the cryostat sits on the beam of charged particles with its horizontal main axis oriented parallel to the beam.
